EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
on vagueness 2

% Look at benchmarks where coverage decreased with increased budget
As expected, both branch coverage and mutation score generally
increased with higher time budgets, although in some cases, specially
at $budget=300s$, a decrease was observed for some benchmarks. Having
run only three repetitions of the tool per time budget, it is fair to
assume the decreases are due to bugs affecting executions with
$budget=300s$ by chance. A preliminary investigation on the source of
this loss of coverage revealed that out-of-memory errors (e.g., for
OKHTTP-2 and RE2J-7), sandboxing problems (e.g., for LA4J-3 and
LA4J-7), and mocking-related issues (e.g., for BCEL-1, BCEL-5, BCEL-7)
are some of the problems in \EVOSUITE.

>>>>

% Look at benchmarks where coverage decreased with increased budget
As expected, both branch coverage and mutation score generally
increased with higher time budgets, although in some cases, specially
with $budget=300s$, a decrease was observed for some
benchmarks. Having run only three repetitions of the tool per time
budget, it is fair to assume the decreases are due to bugs affecting
executions by chance. A preliminary investigation on the source of
this loss of coverage revealed that memory management (e.g.,
out-of-memory errors for OKHTTP-2 and RE2J-7), sandboxing (e.g.,
affecting all executions for LA4J-3 and LA4J-7), and mocking
(affecting BCEL-1, BCEL-5 and BCEL-7, for example) are some of the
aspects that require attention and debugging in \EVOSUITE.
